Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-18 ieee_paper.tex
shrking sect 3

The core of the technique is the use of swizzling and permutation
features of the vectors in the Intel MIC architecture. A vector of 512
bits is composed of four lanes (sometimes called channels) of 128 bits, 
which are made of four segments of 32 bits. A swizzling operation allows
the reorder of the elements within each lane, while a permutation reorders
entire lanes, without changing their contents. 
Figure~\ref{fig:swizzling_permutation}
illustrates these two possibilities. Both permutation and swizzling
support common reordering and broadcast. In the code, the ``permute''
function needs to use the {\tt \_mm512\_permute4f128\_epi32}
instruction which is only defined on integers and therefore in place typecasts
are necessary to convert to a vector to/from the integer type.
\todo{I added a comment stating we preferred swizzling.}
(Note that we prefer swizzling to permutation if possible because we believe 
it is cheaper. Many instructions have swizzling capability, while permuation
is its own instruction. \todo{do we need a reference to my note?})

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/swizzling_lanes.pdf}
  \caption{Swizzling enables the reorder or broadcast of elements within
    each 128 bit group. Permutation enables to reorder or broadcast
    whole 128 bit groups. All lanes must be sizzeled identically.
    \todo{I added to the caption.}}
  \label{fig:swizzling_permutation}
\end{figure}

>>>>

The core of the technique is the use of swizzling and permutation
features of the vectors in the Intel MIC architecture. A vector of 512
bits is composed of four lanes (sometimes called channels) of 128
bits, which are made of four segments of 32 bits. A swizzling
operation allows the reorder of the elements within each lane (see how
{\tt mat} is extracted from {\tt mat\_ent} in
Figure~\ref{code:mat_mul}). While a permutation reorders entire lanes,
without changing their contents (see for instance how {\tt vect} is
generated from {\tt all\_vect} in Figure~\ref{code:mat_mul}).  Both
permutation and swizzling support common reordering and broadcast. In
the code, the ``permute'' function needs to use the {\tt
  \_mm512\_permute4f128\_epi32} instruction which is only defined on
integers and therefore in place typecasts are necessary to convert to
a vector to/from the integer type.  (Note that we prefer swizzling to
permutation if possible because we believe it is cheaper. Many
instructions have swizzling capability, while permuation is its own
instruction. \todo{do we need a reference to intel Xeon phi instruction set?})
